Strings functions analysis

### 2022-08-22 article.tex
clear method removed from table
lang columns added to table

    \begin{table*}[]
        \centering
        \begin{tabular}{|c||c|c|c|c|}
            \hline
            & Popularity & Mutual usages & Mutable O(?) & Immutable O(?) \\ \hline \hline
            capitalize &  &  & 1 & 1 \\ \hline

            char-at &  &  & 1 & 1 \\ \hline

            compare &  &  & n & n \\ \hline

            compare-ignore-case &  &  &  & \\ \hline

            concatenate &  &  & n & n \\ \hline

            containts &  &  & n & n \\ \hline

            count &  &  &  & \\ \hline

            ends-with &  &  & n & n \\ \hline

            equals &  &  & n & n \\ \hline

            find-first &  &  & n & n \\ \hline

            find-last &  &  & n & n \\ \hline

            format &  &  & n & n \\ \hline

            hash &  &  & n & n \\ \hline

            insert &  &  & n & n \\ \hline

            is-alphabetic &  &  & n & n \\ \hline

            is-empty &  &  & 1 & 1 \\ \hline

            is-hexadecimal &  &  & n & n \\ \hline

            is-int &  &  & n & n \\ \hline

            is-lowercase &  &  & n & n \\ \hline

            is-uppercase &  &  & n & n \\ \hline

            is-whitespace &  &  & n & n \\ \hline

            join &  &  & n & n \\ \hline

            length &  &  & 1 & 1 \\ \hline

            matches-regexp &  &  & n & n \\ \hline

            partition &  &  & n & n \\ \hline

            repeat &  &  & n & n \\ \hline

            replace-all &  &  & n & n \\ \hline

            replace-first  &  &  &  & \\ \hline

            split &  &  & n & n \\ \hline

            starts-with &  &  & n & n \\ \hline

            strip &  &  & n & n \\ \hline

            substring &  &  & n & 1 \\ \hline

            swap-case &  &  & n & n \\ \hline

            to-float &  &  & n & n \\ \hline

            to-int &  &  & n & n \\ \hline

            to-lowercase &  &  & n & n \\ \hline

            to-uppercase &  &  & n & n \\ \hline

            trim-left &  &  & n & n \\ \hline

            trim-right &  &  & n & n \\ \hline

            reverse &  &  & n & 1 \\ \hline

            remove &  &  &  & \\ \hline

            uncapitalize &  &  &  & \\ \hline

            as-bytes &  &  &  & \\ \hline

            chop &  &  &  & \\ \hline

            clear &  &  &  & \\ \hline

>>>>

    \begin{table*}[]
        \centering
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            & \begin{sideways}Popularity\end{sideways}
            & \begin{sideways}Mutual usages\end{sideways}
            & \begin{sideways}Mutable O(?)\end{sideways}
            & \begin{sideways}Immutable O(?)\end{sideways}
            \\ \hline \hline
            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\ \hline

            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline

            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline

            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
